---
title: "Preparing Data"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: false
vignette: >
  %\VignetteIndexEntry{Preparing Data}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(HASP)
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               fig.width = 6,
               fig.height = 6)

```


# Introduction

Most examples within `HASP` are given with data obtained via `dataRetrieval` functions. This article describes how to use external (non-`dataRetrieval`) data with `HASP` functions. Users can import their data into R in any of their favorite ways, and use the data frames in any of the scripted work flows. There are 3 main data types used in the `HASP` package: daily data (argument = `gw_level_dv`), field groundwater levels (argument = `gwl`), and water quality data (argument = `qw_data`). 

The `HASP` package provides sample data named `L2701_example_data`. This data is also provided here, in a simplified Microsoft&trade; Excel file:

```{r eval=FALSE}
library(HASP)
system.file("extdata", "sample.xlsx", package = "HASP")
```


We will use the `readxl` package to import this data for these examples. The main idea is import the data, figure out what columns you need, and call the functions appropriately.

## Import the data

This is how to import the sample file. This can be done in any number of ways. The point is to get 3 data frames in your R environment. 

```{r getData}
sample_data_path <- system.file("extdata", "sample.xlsx",
                                package = "HASP")
daily_data <- readxl::read_xlsx(path = sample_data_path, 
                                sheet = "Daily")
names(daily_data)
gwl_data <- readxl::read_xlsx(path = sample_data_path, 
                                sheet = "Field")
names(gwl_data)
qw_data <- readxl::read_xlsx(path = sample_data_path, 
                                sheet = "QW")
names(qw_data)

```

## Call `HASP` functions

```{r}
monthly_frequency_plot(daily_data,
                       date_col = "Date",
                       value_col = "Value",
                       approved_col = "Remark",
                       plot_title = "External Data")

gwl_plot_all(gw_level_dv = daily_data,
             gwl_data =  gwl_data, 
             date_col = c("Date", "Date"),
             value_col = c("Value", "Value"),
             approved_col = c("Remark", "Remark"),
             plot_title = "External Data", 
             add_trend = TRUE)
```

The water-quality plots are less flexible, they require the data frame to have column names "sample_dt", "parm_cd", "result_va", "remark_cd". Renaming columns in R can be done in several ways, here is one using `dplyr`'s `rename` function:

```{r}
library(dplyr)
qw_data <- qw_data %>% 
  rename(sample_dt = Date, 
         parm_cd = parameter,
         result_va = Value,
         remark_cd = Remark)

Sc_Cl_plot(qw_data = qw_data, 
           "External Data")

trend_plot(qw_data, 
           plot_title = "External Data")

```


# Disclaimer

Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.