---
title: "Single Site Water Level"
output: 
  rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Single Site Water Level}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               fig.width = 7,
               fig.height = 6)
library(dplyr)
library(tidyr)
library(ggplot2)
library(HASP)

options(knitr.kable.NA = '')
```

<style>

body {
    max-width: 1600px;
    margin-left:10px;
    padding-left:10px;
}
</style>

This vignette shows how to use `HASP` and other R tools to reproduce:

https://fl.water.usgs.gov/mapper/waterlevel_site_info.php?site=263819081585801


## Site Information

<table>
<tr><td>

```{r siteInfo, results='asis'}
library(HASP)

# siteID <- "263819081585801"
# site_metadata <- site_summary(siteID, markdown = TRUE)
```

</td><td>

```{r whatData}
# data_info <- data_available(siteID)
# kable(data_info)
```

</td></tr> </table>

## Get data using dataRetrieval

Using `dataRetrieval` code to get the data for this site:

```{r getData, eval=TRUE}
library(dataRetrieval)
siteID <- "USGS-263819081585801"
parameterCd <- "62610"
statCd <- "00001"
# Daily data:
gw_level_dv <- read_waterdata_daily(monitoring_location_id = siteID,
                                    parameter_code = parameterCd,
                                    statistic_id = statCd, 
                                    skipGeometry = TRUE)

# Field GWL measured:
gwl_data <- dataRetrieval::read_waterdata_field_measurements(monitoring_location_id = siteID,
                                                             skipGeometry = TRUE)

site_title <- "L -2701\n263819081585801"

y_label <- dataRetrieval::read_waterdata_parameter_codes(parameter_code = parameterCd)$parameter_name

```

## Water Level Data and Analysis

### Weekly frequency

```{r weeklyFrequencyShow}

weekly_frequency_plot(gw_level_dv, 
                      gwl_data = gwl_data,
                      parameter_cd = parameterCd,
                      plot_title = site_title,
                      y_axis_label = y_label)


```



Weekly frequency analysis of daily maximum water level record. Only showing the first 10 rows for this example:

```{r weekly_table}
weekly_table <- weekly_frequency_table(gw_level_dv, 
                                       gwl_data,
                                       parameter_cd = parameterCd)
kable(head(weekly_table, 10), digits = 1)

```


### Daily 2-year

```{r dailyPlotShow, fig.width=9}
daily_gwl_plot(gw_level_dv, 
               gwl_data,
               parameter_cd = parameterCd,
               plot_title = site_title,
               historical_stat = "mean",
               month_breaks = TRUE,
               y_axis_label = y_label)

```


Statistics of maximum daily water level record (DOY = day of year). Only showing the first 10 rows for this example:

```{r dailyShow2}
daily_table <- daily_frequency_table(gw_level_dv, 
                                     gwl_data,
                                     parameter_cd = parameterCd) 

kable(head(daily_table, 10))
```


### Daily value trends


```{r gwlTrendplot}

gwl_plot_all(gw_level_dv, gwl_data, 
             y_label = y_label,
             parameter_cd = parameterCd,
             plot_title = site_title,
             add_trend = TRUE, flip = FALSE)


```

Summary statistics for maximum daily water level measurements:

```{r siteStatsDaily}
siteDV <- site_data_summary(gw_level_dv) 

kable(siteDV, digits = 1)

```

Results of trend analysis on maximum daily water levels:

```{r trendTableDaily}

trend_result <- trend_test(gw_level_dv = gw_level_dv, 
                           gwl_data = NULL,
                           parameter_cd = parameterCd)
kable(trend_result, digits = 1)


```



### Field GWL values



```{r manualPlot}
gwl_plot_all(NULL, gwl_data,
             y_label = y_label,
             parameter_cd = parameterCd,
             plot_title = site_title, 
             flip = FALSE)


```



Summary statistics for manual water level measurements

```{r manualTable}
quantiles <- gwl_data |> 
  site_data_summary(site_col = "monitoring_location_id") 

kable(quantiles, digits = 1)

```


