---
title: "Single Site Data Availability"
output: 
  rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Single Site Data Availability}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               fig.width = 6,
               fig.height = 6)

options(knitr.kable.NA = '')
library(dplyr)
```

<style>

body {
    max-width: 1600px;
    margin-left:10px;
    padding-left:10px;
}
</style>

This vignette shows how to use `HASP` and other R tools to reproduce:

https://fl.water.usgs.gov/mapper/site_info.php?site=263819081585801&stationType=gw

This page merges information from USGS Groundwater Watch website and USGS Water Science Centers.

## Site Information

<table>
<tr><td>

```{r siteInfo, results='asis'}
library(HASP)

siteID <- "263819081585801"
site_metadata <- site_summary(siteID, markdown = TRUE)
```

</td><td>

```{r whatData}
data_info <- data_available(siteID)
kable(data_info)
```

</td></tr> </table>

## Get data using dataRetrieval


<table>
<tr><td>

Using `dataRetrieval` code to get the data for this site:

```{r getData, eval=FALSE}
library(dataRetrieval)
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"
# Daily data:
gw_level_dv <- readNWISdv(siteID,
                          parameterCd,
                          statCd = statCd)

# Periodically measured:
gwl_data <- readNWISgwl(siteID)

# Water quality data:
pcodes_cl_sc <- c("00095","90095","00940","99220")
qw_data <- readNWISqw(siteID,  pcodes_cl_sc)

```

</td><td>

Using the example data provided in the package:

```{r getDataReal}
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"

# Daily
gw_level_dv <-  L2701_example_data$Daily
# Periodic
gwl_data <- L2701_example_data$Discrete
# QW:
qw_data <- L2701_example_data$QW

plot_title <- "L -2701\n263819081585801 "

```

</td></tr> </table>


## Groundwater Data

### Monthly Frequency

```{r monthlyFrequencyPlot, eval=FALSE}

monthly_frequency_plot(gwl_data, 
                       plot_title = plot_title,
                       plot_range = "Past year")

monthly_frequency_table(gwl_data)
```


<table>
<tr><td>

```{r monthlyFreqPlot, echo = FALSE}
monthly_frequency_plot(gwl_data, 
                       plot_title = plot_title,
                       plot_range = "Past year")
```

</td><td>

```{r monthlyFreqTable, echo = FALSE}
monthly_freq_table <- monthly_frequency_table(gwl_data) %>%
  select(month, minMed, p10, p25, p50, p75, p90, maxMed, nYears) %>%
  mutate(month = month.abb[month]) %>%
  rename("Month" = month,
         "Lowest median" = minMed,
         "10th" = p10,
         "25th" = p25,
         "50th" = p50,
         "75th" = p75,
         "Highest median" = maxMed,
         "Number of years" = nYears)
kable(monthly_freq_table, digits = 1)
```


</td></tr> </table>


## Daily 2 year plot

```{r dailyPlot, eval = FALSE}

daily_gwl_2yr_plot(gw_level_dv, 
                   parameterCd, 
                   statCd, 
                   plot_title = plot_title, 
                   month_breaks = TRUE, 
                   historical_stat = "median")

daily_gwl_summary(gw_level_dv, parameterCd, statCd)
```

<table>
<tr><td>

```{r dailyPlotShow, echo = FALSE, fig.width=9}

daily_gwl_2yr_plot(gw_level_dv, 
                   parameterCd, 
                   statCd, 
                   plot_title = plot_title, 
                   month_breaks = TRUE, 
                   historical_stat = "median")
```


</td><td>

```{r dailySummary, echo=FALSE}
daily_summary_table <- daily_gwl_summary(gw_level_dv, parameterCd, statCd) %>%
  select("Begin Date" = begin_date,
         "End Date" = end_date,
         "Days" = days,
         "% Complete" = percent_complete,
         "Lowest Level" = lowest_level,
         "25th" = p25,
         "50th" = p50,
         "75th" = p75,
         "Highest Level" = highest_level)
kable(daily_summary_table)
```

</td></tr> </table>



## Periodic Groundwater Data

```{r periodicPlotDisplay, eval=FALSE}
gwl_plot_periodic(gwl_data, plot_title)

site_data_summary(gwl_data, "sl_lev_va")
```

<table>
<tr><td>

```{r periodicPlot, echo=FALSE}
gwl_plot_periodic(gwl_data, plot_title)
```

</td><td>

```{r periodicTable, echo=FALSE}
sitePeriodic <- site_data_summary(gwl_data, 
                                  "sl_lev_va") %>% 
  select(Minimum = min_site, 	
         `1st` = p25, 
         Median = p50,
         Mean = mean_site,
         `3rd` = p75,
         Maximum = max_site)

kable(sitePeriodic, digits = 1)

```

</td></tr> </table>


### Period of Record - All Data Types

```{r dvPlotDisplay, eval=FALSE}
gwl_plot_all(gw_level_dv, gwl_data, plot_title)

site_data_summary(gw_level_dv, "X_62610_00001")
```

<table>
<tr><td>

```{r dvPlot, echo=FALSE}
gwl_plot_all(gw_level_dv, gwl_data, plot_title)
```

</td><td>

```{r dailyTable, echo=FALSE}
siteDaily <- site_data_summary(gw_level_dv, 
                               "X_62610_00001") %>% 
  select(Minimum = min_site, 	
         `1st` = p25, 
         Median = p50,
         Mean = mean_site,
         `3rd` = p75,
         Maximum = max_site)

kable(siteDaily, digits = 1)

```

</td></tr> </table>

## Salinity Data and Analysis


### Chloride

```{r chloride_plot, eval=FALSE}
trend_plot(qw_data, plot_title = plot_title)

kendell_test_5_20_years(qw_data, 
                        seasonal = TRUE,
                        enough_5 = 1,
                        enough_20 = 1,
                        date_col = "sample_dt",
                        value_col = "result_va")

qw_summary(qw_data, 
           pcode = c("00940","99220"),
           norm_range = c(225,999))
```

<table>
<tr><td>

```{r chloride_plotSHOW, echo=FALSE}
trend_plot(qw_data, plot_title = plot_title)
```

</td><td>

```{r chloride_trend, echo=FALSE}
cl_trend <- kendell_test_5_20_years(qw_data, 
                     seasonal = TRUE,
                     enough_5 = 1,
                     enough_20 = 1,
                     date_col = "sample_dt",
                     value_col = "result_va")
kable(cl_trend, digits = 3)
```

```{r chloride_table, echo=FALSE}
chl_table <- qw_summary(qw_data, 
                       pcode = c("00940","99220"),
                       norm_range = c(225,999))
kable(chl_table)

```



</td></tr> </table>

### Specific Conductance

```{r qwplot1, eval=FALSE}
qw_plot(qw_data, "Specific Conductance", 
        pcode = c("00095", "90095"))
qw_summary(qw_data, 
           pcode = c("00095","90095"),
           norm_range = NA)
```


<table>
<tr><td>

```{r qwplotReal, echo=FALSE}
qw_plot(qw_data, "Specific Conductance", 
        pcode = c("00095", "90095"))
```

</td><td>

```{r sc_table, echo=FALSE}
sc_table <- qw_summary(qw_data, 
                       pcode = c("00095","90095"),
                       norm_range = NA)
kable(sc_table)

```


</td></tr> </table>


### Specific Conductance vs Chloride

```{r salityPlot, eval=FALSE}
Sc_Cl_plot(qw_data, plot_title = plot_title)

Sc_Cl_table(qw_data)
```

<table>
<tr><td>

```{r salityPlotDisplay, echo=FALSE}
Sc_Cl_plot(qw_data, plot_title = plot_title)

```


</td><td>

```{r salityTable, echo=FALSE}
sc_cl <- Sc_Cl_table(qw_data)

# only show 10 row:
kable(head(sc_cl, 10), 
      col.names = c("Date",
                    "Chloride [mg/L]",
                    "Specific conductance [µS/L]"))
```


</td></tr> </table>


