---
title: "Single Site Data Availability"
output: 
  rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Single Site Data Availability}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               warning = FALSE,
               message = FALSE,
               fig.width = 7,
               fig.height = 7)
library(dplyr)
library(tidyr)
library(ggplot2)
library(HASP)

options(knitr.kable.NA = '')
```


This vignette shows how to use `HASP` and other R tools to reproduce:

https://fl.water.usgs.gov/mapper/site_info.php?site=263819081585801&stationType=gw

This page merges information from USGS Groundwater Watch website and USGS Water Science Centers.

First, use the `dataRetrieval` package to get site information:

## DESCRIPTION

```{r siteInfo, echo=TRUE, results='asis'}
library(dataRetrieval)
library(HASP)
library(dplyr)
library(tidyr)

siteID <- "263819081585801"
site_metadata <- site_summary(siteID, markdown = TRUE)
```

## AVAILABLE DATA

```{r whatData, echo=TRUE}
data_info <- data_available(siteID)
kable(data_info)
```

## Site Statistics

## Daily Groundwater Data

## Periodic Groundwater Data

## Period of Record - All Data Types

## Salinity Data and Analysis

```{r salityPlot, echo=TRUE}
parameterCd <- c("00095","90095","00940","99220")
site_data <- readNWISqw(siteID,  parameterCd)

Sc_Cl_plot(site_data, title = siteID)

```

```{r salityTable, echo=TRUE}
parameterCd <- c("00095","90095","00940","99220")
site_data <- readNWISqw(siteID,  parameterCd)

sc_cl <- Sc_Cl_table(site_data)

# only show 10 row:
kable(head(sc_cl, 10), 
      col.names = c("Date",
                    "Chloride [mg/L]",
                    "Specific conductance [µS/L]"))
```

