---
title: "Single Site Water Level"
output: 
  rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Single Site Water Level}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               fig.width = 7,
               fig.height = 6)
library(dplyr)
library(tidyr)
library(ggplot2)
library(HASP)

options(knitr.kable.NA = '')
```

<style>

body {
    max-width: 1600px;
    margin-left:10px;
    padding-left:10px;
}
</style>

This vignette shows how to use `HASP` and other R tools to reproduce:

https://fl.water.usgs.gov/mapper/waterlevel_site_info.php?site=263819081585801


## Site Information

<table>
<tr><td>

```{r siteInfo, results='asis'}
library(HASP)

siteID <- "263819081585801"
site_metadata <- site_summary(siteID, markdown = TRUE)
```

</td><td>

```{r whatData}
data_info <- data_available(siteID)
kable(data_info)
```

</td></tr> </table>

## Get data using dataRetrieval


<table>
<tr><td>

Using `dataRetrieval` code to get the data for this site:

```{r getData, eval=TRUE}
library(dataRetrieval)
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"
# Daily data:
gw_level_dv <- readNWISdv(siteID,
                          parameterCd,
                          statCd = statCd)

# Field GWL measured:
gwl_data <- readNWISgwl(siteID)

site_title <- "L -2701\n263819081585801"

```

</td><td>

Using the example data provided in the package:

```{r getDataReal, eval=FALSE}
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"

# Daily
gw_level_dv <-  L2701_example_data$Daily
# Field
gwl_data <- L2701_example_data$Discrete

```

</td></tr> </table>

## Water Level Data and Analysis

### Weekly frequency

```{r weeklyFrequencyShow}

weekly_frequency_plot(gw_level_dv, 
                      parameter_cd = parameterCd,
                      plot_title = site_title,
                      y_axis_label = "Groundwater level above NGVD 1929, feet")


```



Weekly frequency analysis of daily maximum water level record. Only showing the first 10 rows for this example:

```{r weekly_table}
weekly_table <- weekly_frequency_table(gw_level_dv, 
                                       parameter_cd = parameterCd)
kable(head(weekly_table, 10), digits = 1)

```


### Daily 2-year

```{r dailyPlotShow, fig.width=9}
daily_gwl_2yr_plot(gw_level_dv, 
                   parameter_cd = parameterCd,
                   plot_title = site_title,
                   historical_stat = "mean",
                   month_breaks = TRUE,
                   y_axis_label = "Groundwater level above NGVD 1929, feet")

```


Statistics of maximum daily water level record (DOY = day of year). Only showing the first 10 rows for this example:

```{r dailyShow2}
daily_table <- daily_frequency_table(gw_level_dv, 
                                     parameter_cd = parameterCd) 

kable(head(daily_table, 10))
```


### Daily value trends


```{r gwlTrendplot}
y_label <- dataRetrieval::readNWISpCode(parameterCd)$parameter_nm


gwl_plot_all(gw_level_dv, gwl_data, 
             y_label = y_label,
             parameter_cd = parameterCd,
             plot_title = site_title,
             add_trend = TRUE, flip_y = FALSE)


```

Summary statistics for maximum daily water level measurements:

```{r siteStatsDaily}
siteDV <- gw_level_dv %>%
  rename(value = X_62610_00001) %>% 
  site_data_summary() 

kable(siteDV, digits = 1)

```

Results of trend analysis on maximum daily water levels:

```{r trendTableDaily}
gw_monthly <- monthly_mean(gw_level_dv)

trend_result <- kendell_test_5_20_years(gw_monthly, 
                        seasonal = TRUE, 
                        date_col = "mid_date", 
                        value_col = "mean_va")
kable(trend_result, digits = 1)


```



### Field GWL values



```{r manualPlot}
gwl_plot_all(NULL, gwl_data,
             y_label = y_label,
             parameter_cd = parameterCd,
             plot_title = site_title, 
             flip_y = FALSE)


```



Summary statistics for manual water level measurements

```{r manualTable}
quantiles <- gwl_data %>% 
  rename(value = sl_lev_va) %>% 
  site_data_summary() 

kable(quantiles, digits = 1)

```


