---
title: "Single Site Water Level"
output: 
  rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Water Level Single Site Information}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               fig.width = 6,
               fig.height = 6)
library(dplyr)
library(tidyr)
library(ggplot2)
library(HASP)

options(knitr.kable.NA = '')
```

<style>

body {
    max-width: 1600px;
    margin-left:10px;
    padding-left:10px;
}
</style>

This vignette shows how to use `HASP` and other R tools to reproduce:

https://fl.water.usgs.gov/mapper/waterlevel_site_info.php?site=263819081585801


## Site Information

<table>
<tr><td>

```{r siteInfo, results='asis'}
library(HASP)

siteID <- "263819081585801"
site_metadata <- site_summary(siteID, markdown = TRUE)
```

</td><td>

```{r whatData}
data_info <- data_available(siteID)
kable(data_info)
```

</td></tr> </table>

## Get data using dataRetrieval


<table>
<tr><td>

Using `dataRetrieval` code to get the data for this site:

```{r getData, eval=TRUE}
library(dataRetrieval)
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"
# Daily data:
gw_level_dv <- readNWISdv(siteID,
                          parameterCd,
                          statCd = statCd)

# Field GWL measured:
gwl_data <- readNWISgwl(siteID)

site_title <- "L -2701\n263819081585801"

```

</td><td>

Using the example data provided in the package:

```{r getDataReal, eval=FALSE}
siteID <- "263819081585801"
parameterCd <- "62610"
statCd <- "00001"

# Daily
gw_level_dv <-  L2701_example_data$Daily
# Field
gwl_data <- L2701_example_data$Discrete

```

</td></tr> </table>

## Water Level Data and Analysis

### Weekly frequency

```{r weeklyFrequencyShow, eval=FALSE}

weekly_frequency_plot(gw_level_dv, 
                      date_col = "Date",
                      value_col = "X_62610_00001",
                      approved_col = "X_62610_00001_cd",
                      plot_title = site_title,
                      y_axis_label = "Groundwater level above NGVD 1929, feet")

weekly_table <- weekly_frequency_table(gw_level_dv, 
                                       date_col = "Date",
                                       value_col = "X_62610_00001",
                                       approved_col = "X_62610_00001_cd")

head(weekly_table, 10)
```


<table>
<tr><td>
```{r weeklyFrequencyPlot, echo=FALSE, fig.width=9}
weekly_frequency_plot(gw_level_dv, 
                      date_col = "Date",
                      value_col = "X_62610_00001",
                      approved_col = "X_62610_00001_cd",
                      plot_title = site_title,
                      y_axis_label = "Groundwater level above NGVD 1929, feet")

```

</td><td>

Weekly frequency analysis of daily maximum water level record. Only showing the first 10 rows for this example:

```{r weekly_table, echo=FALSE}
library(dplyr)

weekly_freq_table <- weekly_frequency_table(gw_level_dv,
                                            date_col = "Date",
                                            value_col = "X_62610_00001",
                                            approved_col = "X_62610_00001_cd") %>%
  select("Week" = week,
         "Lowest median" = minMed,
         "10th" = p10,
         "25th" = p25,
         "50th" = p50,
         "75th" = p75,
         "90th" = p90,
         "Highest median" = maxMed,
         "# Years" = nYears)
kable(head(weekly_freq_table, 10), digits = 1)

```


</td></tr> </table>


### Daily 2-year

```{r dailyPlotShow, eval=FALSE}
daily_gwl_2yr_plot(gw_level_dv, 
                   date_col = "Date",
                   value_col = "X_62610_00001",
                   approved_col = "X_62610_00001_cd",
                   plot_title = site_title,
                   historical_stat = "mean",
                   month_breaks = TRUE,
                   y_axis_label = "Groundwater level above NGVD 1929, feet")

daily_table <- daily_frequency_table(gw_level_dv, 
                      date_col = "Date",
                      value_col = "X_62610_00001",
                      approved_col = "X_62610_00001_cd")
head(daily_table, n = 10)
```

<table>
<tr><td>

```{r dailyDo, echo=FALSE, fig.width=9}
daily_gwl_2yr_plot(gw_level_dv, 
                   date_col = "Date",
                   value_col = "X_62610_00001",
                   approved_col = "X_62610_00001_cd",
                   plot_title = site_title,
                   historical_stat = "mean",
                   month_breaks = TRUE,
                   y_axis_label = "Groundwater level above NGVD 1929, feet")

```

</td><td>

Statistics of maximum daily water level record (DOY = day of year). Only showing the first 10 rows for this example:

```{r dailyShow2, echo=FALSE}
daily_table <- daily_frequency_table(gw_level_dv, 
                                     date_col = "Date",
                                     value_col = "X_62610_00001",
                                     approved_col = "X_62610_00001_cd") %>%
  rename("DOY" = DOY,
         "Maximum" = max,
         "Mean" = mean,
         "Minimum" = min,
         "# Points" = points)
kable(head(daily_table, 10))
```

</td></tr> </table>

### Daily value trends

```{r trend_dv, eval=FALSE}
y_label <- dataRetrieval::readNWISpCode("62610")$parameter_nm

gwl_plot_all(gw_level_dv, 
             gwl_data, 
             y_label = y_label,
             date_col = c("Date", "lev_dt"),
             value_col = c("X_62610_00001",
                           "sl_lev_va"),
             approved_col = c("X_62610_00001_cd",
                              "lev_age_cd"),
             plot_title = site_title,
             add_trend = TRUE, flip_y = FALSE)

site_data_summary(gw_level_dv, "X_62610_00001")

gw_monthly <- monthly_mean(gw_level_dv)

kendell_test_5_20_years(gw_monthly, 
                        seasonal = TRUE, 
                        date_col = "mid_date", 
                        value_col = "mean_va")
```


<table>
<tr><td>

```{r gwlTrendplot, echo=FALSE}
y_label <- dataRetrieval::readNWISpCode("62610")$parameter_nm


gwl_plot_all(gw_level_dv, gwl_data, 
             y_label = y_label,
             date_col = c("Date", "lev_dt"),
             value_col = c("X_62610_00001",
                           "sl_lev_va"),
             approved_col = c("X_62610_00001_cd",
                              "lev_age_cd"),
             plot_title = site_title,
             add_trend = TRUE, flip_y = FALSE)


```

</td><td>

Summary statistics for maximum daily water level measurements:

```{r siteStatsDaily, echo=FALSE}
siteDV <- site_data_summary(gw_level_dv, "X_62610_00001") %>% 
  select(Minimum = min_site, 	
         `1st` = p25, 
         Median = p50,
         Mean = mean_site,
         `3rd` = p75,
         Maximum = max_site)

kable(siteDV, digits = 1)

```

Results of trend analysis on maximum daily water levels:

```{r trendTableDaily, echo=FALSE}
gw_monthly <- monthly_mean(gw_level_dv)

trend_result <- kendell_test_5_20_years(gw_monthly, 
                        seasonal = TRUE, 
                        date_col = "mid_date", 
                        value_col = "mean_va")
kable(trend_result, digits = 1)


```

</td></tr> </table>

### Field GWL values

```{r manual, eval=FALSE}
gwl_plot_all(NULL, gwl_data,
             y_label = y_label,
             date_col = "lev_dt",
             value_col = "sl_lev_va",
             approved_col = "lev_age_cd",
             plot_title = site_title, 
             flip_y = FALSE)

site_data_summary(gwl_data, "sl_lev_va")
```

<table>
<tr><td>

```{r manualPlot, echo=FALSE}
gwl_plot_all(NULL, gwl_data,
             y_label = y_label,
             date_col = "lev_dt",
             value_col = "sl_lev_va",
             approved_col = "lev_age_cd",
             plot_title = site_title, 
             flip_y = FALSE)


```

</td><td>

Summary statistics for manual water level measurements

```{r manualTable, echo=FALSE}
quantiles <- site_data_summary(gwl_data, "sl_lev_va") %>% 
  select(Minimum = min_site, 	
         `1st` = p25, 
         Median = p50,
         Mean = mean_site,
         `3rd` = p75,
         Maximum = max_site)
kable(quantiles, digits = 1)

```

</td></tr> </table>

